\documentclass[12pt]{article}
\usepackage{a4wide}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[danish]{babel}
\usepackage[pdftex]{graphicx}
\usepackage{pdfpages}
\usepackage{listings}

\title{4\_PETCT\_AC\_Brain.Adult}

\begin{document}
\pagenumbering{roman}
\maketitle
\newpage
\tableofcontents
\newpage
\pagenumbering{arabic}


\section{Topogram}
\subsection{Routine}
 \begin{itemize}\item mA: 35\item kV: 120\item Topogram length: 256 mm\item Tube position: Lateral
\subsection{Scan}
\item mA: 35\item kV: 120\item Delay: 4s\item Topogram length: 256 mm\item Direction: Craniocaudal\item Tube position: Lateral\item API: ""\item Kernel: T20s\item Window: Topogra
\section{CT WB}
\subsection{Routine}
\item Eff. mAs: 170\item kV: 120\item CARE Dose4D: Off\item CTDlvol: 29.597mGy\item Scan time: 20.050 s\item Delay: 2.000 s\item Slice: 3 mm\item No. of images: Samme som i foerste recon, slet?(y/n)\item Tilt: 0.0 grader
\subsection{Scan}
\item Quality ref. mAs: 350\item Eff. mAs: 170\item kV: 120\item Scan time: 20.050 s\item Rotation time: 1.000 s\item Delay: 2.000 s\item Slice: 3 mm\item Pitch: 1.00\item Direction: Craniocaudal
\subsection{Recon}

\subsubsection{Recon 1}
\item Series description: tmp CT Brain RTD
\item Slice: 4
\item Kernel: "H19s"
\item Window: "Cerebrum"
\item Extended FoV: false
\item FoV: 300
\item Center X: 0
\item Center Y: 0
\item Mirroring: None
\item Extended CT scale: Standard
\item Recon job: Axial
\item Recon Axis: Axial
\item Image order: Caudocranial
\item Recon increment: 4.000
\item No. of images: 56
\subsubsection{Recon 2}
\item Series description: AC CT Brain
\item Slice: 3
\item Kernel: "H19s"
\item Window: "Cerebrum"
\item Extended FoV: false
\item FoV: 300
\item Center X: 0
\item Center Y: 0
\item Mirroring: None
\item Extended CT scale: Standard
\item Recon job: Axial
\item Recon Axis: Axial
\item Image order: Caudocranial
\item Recon increment: 1.500
\item No. of images: 148
\section{Pause}

\section{PET WB}
\subsection{Routine}
\item Isotope: F-18
\item Pharm.: Fluorodeoxyglucose
\item Inj. Dose: 1 
\item Inj. date (date/month - year): 02/10 - 2008
\item Inj. time: 07:16:19
\item Scan mode: Sinogram
\item Scan range: Match CT FOV
\item No. of beds: N/A
\item Scan duration/bed: 10.000000 Minutes
\subsection{Scan}
\item Autoload: true
\item Rebinner LUT: N/A
\item Scan output: Sinogram
\item Sinogram mode: false
\item Input trigger signal: None
\item LLD (keV): N/A
\item ULD (keV): N/A
\subsection{Recon}

\subsubsection{Recon 1}
\item Series description: PET Brain
\item Recon range (bed): ups..
\item Output image type: Corrected
\item Recon method: Iterative3D
\item Iterations: 4
\item Subsets: 24
\item Image size: 400
\item Zoom: 2.000000
\item Filter: Gaussian
\item FWHM (mm): 4.000000
\item Offset X: 0 mm
\item Offset Y: 0 mm
\item Attenuation correction: On (1)
\item Scatter correction: true
\item Match CT slice location: true
\item Save intermediate data: false
\end{itemize}
\end{document}