\documentclass[12pt]{article}
\usepackage{a4wide}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[danish]{babel}
\usepackage[pdftex]{graphicx}
\usepackage{pdfpages}
\usepackage{listings}

\title{Hjerne\_Dotatoc\_PET\_5.MlAdult}

\begin{document}
\pagenumbering{roman}
\maketitle
\newpage
\tableofcontents
\newpage
\pagenumbering{arabic}


\begin{itemize}\section{Topogram}
\subsection{Routine}
\item mA: 35\item kV: 120\item Topogram length: 256 mm\item Tube position: Lateral
\subsection{Scan}\item mA: 35\item kV: 120\item Delay: 4s\item Topogram length: 0 mm\item Direction: Craniocaudal\item Tube position: Lateral\item API: None\item Kernel: 20s standar\item Window: Topogram Head
\section{CT Brain}
\subsection{Routine}
\item Eff. mAs: 30\item kV: 120\item CARE Dose4D: Off\item CareDoseType: CareDoseAEC\item CTDlvol: 4.12323mGy\item Scan time: 8.010 s\item Delay: 4.000 s\item Slice: 3.00 mm\item No. of images: Samme som i foerste recon, slet?(y/n)\item Tilt: 30 grader
\subsection{Scan}
\item Quality ref. mAs: 380\item Eff. mAs: 30\item kV: 120\item Scan time: 8.010 s\item Rotation time: 1.000 s\item Delay: 4.000 s\item Slice: 3.00 mm\item Pitch: 1.2000000\item Direction: Caudocranial\subsection{Recons}

\subsubsection{Recon 1}
\item Series description: AC CT
\item Slice: 3.00
\item Kernel: H19s PET very smooth
\item Window: Cerebrum
\item Extended FoV: Off
\item FoV: 300
\item Center X: 0
\item Center Y: 0
\item Mirroring: None
\item Extended CT scale: Standard
\item Recon job: Axial
\item Recon Axis: Axial
\item Image order: Caudocranial
\item Recon increment: 3.000
\item No. of images: 74
\section{Pause}
\section{PET Brain}\subsection{Routine}
\item Isotope: Ga-68
\item Pharm.: Dotatoc
\item Inj. Dose: 1 MegaBequerels
\item Inj. date (date/month - year): 15/05 - 2012
\item Inj. time: 09:34:00
\item Scan mode: List mode
\item Scan range: Match CT FOV
\item No. of beds: 1
\item Scan duration/bed: 15 Minutes
\subsection{Scan}
\item Autoload: On
\item Rebinner LUT: Off
\item Scan output: List mode
\item Sinogram mode: Trues
\item Input trigger signal: None
\item LLD (keV): 435
\item ULD (keV): 650
\subsection{Recons}
\subsubsection{Recon 1}
\item Series description: PET Brain corrected 3 mm zoom 3
\item Recon range (bed): Automatic/All/dunno
\item Output image type: NoRecon
\item Recon method: Iterative3D
\item Iterations: 6
\item Subsets: 16
\item Image size: 336
\item Zoom: 3
\item Filter: Gaussian
\item FWHM (mm): 3
\item Offset X: 0 mm
\item Offset Y: 0 mm
\item Attenuation correction: On (1)
\item Scatter correction: On
\item Match CT slice location: On
\item Save intermediate data: Off
\end{itemize}
\end{document}