\documentclass[12pt]{article}
\usepackage{a4wide}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[danish]{babel}
\usepackage[pdftex]{graphicx}
\usepackage{pdfpages}
\usepackage{listings}
\usepackage{enumitem}
\usepackage[compact]{titlesec}

\title{Hjerne\_FDG\_PET\_barn\_4.Child\_PET4}

\begin{document}
\pagenumbering{roman}
\maketitle
\newpage
\tableofcontents
\newpage
\pagenumbering{arabic}


\begin{itemize}[noitemsep]\section{Topogram}
\subsection{Routine}
\item mA: 50\item kV: 80\item Topogram length: 256 mm\item Tube position: Lateral
\subsection{Scan}\item mA: 50\item kV: 80\item Delay: 4s\item Topogram length: 256 mm\item Direction: Craniocaudal\item Tube position: Lateral\item API: API \item Kernel: 20\item Window: Topogram
\section{Lav dosis CT}
\subsection{Routine}
\item Eff. mAs: 30\item kV: 80\item CARE Dose4D: On\item CareDoseType: CareDoseAEC\item CTDlvol: 1.43979mGy\item Scan time: 13.125 s\item Delay: 2.000 s\item Slice: 2 mm\item No. of images: Samme som i foerste recon, slet?(y/n)\item Tilt: 0.0 grader
\subsection{Scan}
\item Quality ref. mAs: 30\item Eff. mAs: 30\item kV: 80\item Scan time: 13.125 s\item Rotation time: 1.000 s\item Delay: 2.000 s\item Slice: 2 mm\item Pitch: 1.00\item Direction: Caudocranial\subsection{Recons}

\subsubsection{Recon 1}
\item Series description: Lav dosis CT RTD
\item Slice: 4
\item Kernel: H19s
\item Window: Cerebrum
\item Extended FoV: Off
\item FoV: 300
\item Center X: 0
\item Center Y: 0
\item Mirroring: None
\item Extended CT scale: Standard
\item Recon job: Axial
\item Recon Axis: Axial
\item Image order: Caudocranial
\item Recon increment: 4.000
\item No. of images: 56
\subsubsection{Recon 2}
\item Series description: AC  CT
\item Slice: 2
\item Kernel: H19s
\item Window: Cerebrum
\item Extended FoV: Off
\item FoV: 300
\item Center X: 0
\item Center Y: 0
\item Mirroring: None
\item Extended CT scale: Standard
\item Recon job: Axial
\item Recon Axis: Axial
\item Image order: Caudocranial
\item Recon increment: 2.000
\item No. of images: 111
\section{Pause}
\section{PET Hjerne}\subsection{Routine}
\item Isotope: F-18
\item Pharm.: Fluorodeoxyglucose
\item Inj. Dose: 0 Bequerels
\item Scan mode: Sinogram
\item Scan range: Do not match CT FOV
\item No. of beds: Not given. Check recon range
\item Scan duration/bed: 10.000000 Minutes
\subsection{Scan}
\item Autoload: On
\item Rebinner LUT: Off
\item Scan output: Sinogram
\item Sinogram mode: false
\item Input trigger signal: None
\item LLD (keV): n/a
\item ULD (keV): n/a
\subsection{Recons}
\subsubsection{Recon 1}
\item Series description: PET Hjerne
\item Recon range (bed): 1 to 1
\item Output image type: Corrected
\item Recon method: Iterative3D
\item Iterations: 4
\item Subsets: 24
\item Image size: 400
\item Zoom: 2.000000
\item Filter: Gaussian
\item FWHM (mm): 4.000000
\item Offset X: 0 mm
\item Offset Y: 0 mm
\item Attenuation correction: Off ()
\item Scatter correction: On
\item Match CT slice location: On
\item Save intermediate data: Off
\end{itemize}
\end{document}