\documentclass[12pt]{article}
\usepackage{a4wide}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[danish]{babel}
\usepackage[pdftex]{graphicx}
\usepackage{pdfpages}
\usepackage{listings}

\title{PET\_AC\_WB\_FDG.MlChild}

\begin{document}
\pagenumbering{roman}
\maketitle
\newpage
\tableofcontents
\newpage
\pagenumbering{arabic}


\section{Topogram}
\subsection{Routine}
 \begin{itemize}\item mA: 50\item kV: 80\item Topogram length: 0 mm\item Tube position: Top
\subsection{Scan}
\item mA: 50\item kV: 80\item Delay: 4s\item Topogram length: 0 mm\item Direction: Craniocaudal\item Tube position: Top\item API: None\item Kernel: T20s standard\item Window: Topogram Body
\section{CT WB}
\subsection{Routine}
\item Eff. mAs: 30\item kV: 11\item CARE Dose4D: Off\item CTDlvol: 0.540268mGy\item Scan time: 1.4000000 s\item Delay: 4.000 s\item Slice: 3.00 mm\item No. of images: Samme som i foerste recon, slet?(y/n)\item Tilt: 30 grader
\subsection{Scan}
\item Quality ref. mAs: 25\item Eff. mAs: 30\item kV: 80.\item Scan time: 11.000 s\item Rotation time: 0.500 s\item Delay: 4.000 s\item Slice: 0.6 mm\item Pitch: 1.4000000\item Direction: Craniocaudal
\subsection{Recon}

\subsubsection{Recon 1}
\item Series description: AC CT lavdosis
\item Slice: 3.00
\item Kernel: "B19f PET very smooth"
\item Window: "Baby Abdomen"
\item Extended FoV: On
\item FoV: 700
\item Center X: 0
\item Center Y: 0
\item Mirroring: None
\item Extended CT scale: Standard
\item Recon job: Axial
\item Recon Axis: Axial
\item Image order: Craniocaudal
\item Recon increment: 3.000
\item No. of images: 274
\section{Pause}

\section{PET WB}
\subsection{Routine}
\item Isotope: F-18
\item Pharm.: FDG
\item Inj. Dose: 1 MegaBequerels
\item Inj. date (date/month - year): 08/05 - 2012
\item Inj. time: 17:05:00
\item Scan mode: Sinogram
\item Scan range: Match CT FOV
\item No. of beds: 5
\item Scan duration/bed: 2 PtMinute
\subsection{Scan}
\item Autoload: On
\item Rebinner LUT: Off
\item Scan output: Sinogram
\item Sinogram mode: Trues
\item Input trigger signal: None
\item LLD (keV): 425
\item ULD (keV): 650
\subsection{Recon}

\subsubsection{Recon 1}
\item Series description: PET WB corrected 
\item Recon range (bed): ups..
\item Output image type: Corrected
\item Recon method: Iterative
\item Iterations: 4
\item Subsets: 8
\item Image size: 168
\item Zoom: 1
\item Filter: Gaussian
\item FWHM (mm): 4
\item Offset X: 0 mm
\item Offset Y: 0 mm
\item Attenuation correction: On (1)
\item Scatter correction: On
\item Match CT slice location: On
\item Save intermediate data: Off
\subsubsection{Recon 2}
\item Series description: PET WB True X
\item Recon range (bed): ups..
\item Output image type: Corrected
\item Recon method: TrueX
\item Iterations: 2
\item Subsets: 21
\item Image size: 336
\item Zoom: 1
\item Filter: Gaussian
\item FWHM (mm): 2
\item Offset X: 0 mm
\item Offset Y: 0 mm
\item Attenuation correction: On (1)
\item Scatter correction: Off
\item Match CT slice location: On
\item Save intermediate data: Off
\end{itemize}
\end{document}