\documentclass[12pt]{article}
\usepackage{a4wide}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[danish]{babel}
\usepackage[pdftex]{graphicx}
\usepackage{pdfpages}
\usepackage{listings}

\title{PETCT\_NEMA\_2007\_IQ.Adult\_PET4}

\begin{document}
\pagenumbering{roman}
\maketitle
\newpage
\tableofcontents
\newpage
\pagenumbering{arabic}


\begin{itemize}\section{Topogram}
\subsection{Routine}
\item mA: 35\item kV: 120\item Topogram length: 1024 mm\item Tube position: Top
\subsection{Scan}\item mA: 35\item kV: 120\item Delay: 4s\item Topogram length: 1024 mm\item Direction: Craniocaudal\item Tube position: Top\item API: API \item Kernel: 80\item Window: Topogram
\section{AC CT NEMA}
\subsection{Routine}
\item Eff. mAs: 50\item kV: 120\item CARE Dose4D: Off\item CareDoseType: CareDoseAEC\item CTDlvol: 3.64mGy\item Scan time: 8.050 s\item Delay: 2.000 s\item Slice: 5 mm\item No. of images: Samme som i foerste recon, slet?(y/n)\item Tilt: 0.0 grader
\subsection{Scan}
\item Quality ref. mAs: 120\item Eff. mAs: 50\item kV: 120\item Scan time: 8.050 s\item Rotation time: 0.500 s\item Delay: 2.000 s\item Slice: 5 mm\item Pitch: 0.80\item Direction: Craniocaudal\subsection{Recons}

\subsubsection{Recon 1}
\item Series description: tmp AC CT NEMA RTD
\item Slice: 4
\item Kernel: B19f
\item Window: Abdomen
\item Extended FoV: Off
\item FoV: 500
\item Center X: 0
\item Center Y: 0
\item Mirroring: None
\item Extended CT scale: Standard
\item Recon job: Axial
\item Recon Axis: Axial
\item Image order: Craniocaudal
\item Recon increment: 4.000
\item No. of images: 56
\subsubsection{Recon 2}
\item Series description: AC CT NEMA
\item Slice: 5
\item Kernel: B19f
\item Window: Abdomen
\item Extended FoV: On
\item FoV: 780
\item Center X: 0
\item Center Y: 0
\item Mirroring: None
\item Extended CT scale: Standard
\item Recon job: Axial
\item Recon Axis: Axial
\item Image order: Craniocaudal
\item Recon increment: 3.000
\item No. of images: 75
\section{Pause}
\section{PET NEMA IQ}\subsection{Routine}
\item Isotope: F-18
\item Pharm.: Fluorodeoxyglucose
\item Inj. Dose: 370000000 Bequerels
\item Inj. date (date/month - year): 28/10 - 2009
\item Inj. time: 14:49:29
\item Scan mode: Sinogram
\item Scan range: Do not match CT FOV
\item No. of beds: Not given. Check recon range
\item Scan duration/bed: 7.600000 Minutes
\subsection{Scan}
\item Autoload: On
\item Rebinner LUT: Off
\item Scan output: Sinogram
\item Sinogram mode: false
\item Input trigger signal: None
\item LLD (keV): n/a
\item ULD (keV): n/a
\subsection{Recons}
\subsubsection{Recon 1}
\item Series description: PET NEMA IQ
\item Recon range (bed): Automatic/All/dunno
\item Output image type: Corrected
\item Recon method: Iterative3D
\item Iterations: 2
\item Subsets: 24
\item Image size: 200
\item Zoom: 1
\item Filter: Gaussian
\item FWHM (mm): 5
\item Offset X: 0 mm
\item Offset Y: 0 mm
\item Attenuation correction: Off ()
\item Scatter correction: On
\item Match CT slice location: Off
\item Save intermediate data: Off
\end{itemize}
\end{document}